Incentivizing Exploration with Heterogeneous Utilities

### 2017-11-27 paper.tex
Fix to proof of Lemma 1

\subsection{Assumptions}
In this secion, we state several assumptions assumed by our analysis.  First define
\begin{align}
\Omega_{i,j}=\{\theta:B(\theta)=i, \hat{B}(\theta)=j\}, \nonumber 
\end{align}
which is the set of agent preferences whose best arm is arm $i$ and second best arm is arm $j$. With this definition, our analysis makes the following assumptions:

@@

In this section, we prove using Algorithm~\ref{Alg1}, we can achieve $O(N^2+M(\log(T))^2)$ regret bound with $O(N)$ payment budget, where $M$ bounds the density of agents who are indifferent between their best and second best arm.

Before we start our analysis, we need the following notations. Denote $S(\delta)$ as the proportion of user whose utility difference between their best arm and the second best arm is less than $\delta$. Formally, $S(\delta)=P(\theta: \theta \cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}\leq \delta)$. Denote $p(\delta)=\min_{i}P(\{\theta:\theta\cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}>\delta\})$. Based on $p(\delta)$'s definition, we know $p(0)=p$.

With the help of our assumptions and the above notations, we now state our main results:

@@

Before we prove our main results, we need to prove several lemmas. First, based on Assumption~\ref{A1}, we can get the following bound for $S(\delta)$.

@@

\begin{proof}
\begin{align}
S(\delta)&=\sum_{B(\theta)=i}\sum_{\hat{B}(\theta)=j}P(\{\theta(u_{i}-u_{j})<\delta\}) \nonumber \\
&=\sum_{B(\theta)=i}\sum_{\hat{B}(\theta)=j}P(\{\theta(u_{i}-u_{j})<\delta|\theta\in \Omega_{i,j}\})P(\theta\in \Omega_{i,j}) \nonumber \\
&\leq \sum_{B(\theta)=i}\sum_{\hat{B}(\theta)=j}M\delta \times P(\theta\in \Omega_{i,j}) \nonumber \\
&=M\delta \nonumber 
\end{align}
\end{proof}

>>>>

\subsection{Assumptions}
In this section, we state several assumptions assumed by our analysis.  First define
\begin{align}
\Omega_{i,j}=\{\theta:B(\theta)=i, \hat{B}(\theta)=j\}, \nonumber 
\end{align}
which is the set of agent preferences whose best arm is arm $i$ and second best arm is arm $j$. With this definition, our analysis makes the following assumptions:

@@

In this section, we prove Algorithm~\ref{Alg1} achieves $O(N^2+M(\log(T))^2)$ cumulative regret with $O(N)$ payment budget.  This is stated in the following pair of theorems, which together constitute our main results.

@@

Before we prove these two theorems, we must first introduce two additional pieces of notation, which will be used in preliminary lemmas.  Let $S(\delta)$ be the proportion of users whose utility difference between their best and second best arm is less than $\delta$. Formally, $S(\delta)=P(\theta: \theta \cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}\leq \delta)$. Then, let $p(\delta)=\min_{i}P(\{\theta:\theta\cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}>\delta\})$. We know $p(0)=p$.

With this additional notation, we now prove several lemmas.
First, based on Assumption~\ref{A1}, we have the following bound for $S(\delta)$.

@@

\begin{proof}
\begin{align*}
S(\delta)
&=\sum_{i,j}P(\theta\cdot(u_{i}-u_{j})<\delta|\theta\in \Omega_{i,j})P(\theta\in \Omega_{i,j}) \\
&\leq \sum_{i,j}M\delta \times P(\theta\in \Omega_{i,j}) \\
&=M\delta.
\end{align*}
\end{proof}
